% !TEX TS-program = pdflatex
\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{kotex}
\usepackage{hyperref}
\usepackage{fancyhdr}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.35em}
\setlength{\headheight}{26pt}
\setlist[itemize]{leftmargin=1.5em, itemsep=0.3em, topsep=0.1em}
\titleformat{\section}{\Large\scshape}{}{0pt}{}[\vspace{0.3em}\titlerule]
\titlespacing*{\section}{0pt}{1.6em}{0.9em}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[R]{\itshape Seth Seokhee Han --- Curriculum Vitae \\ Updated on: 11/02/2025}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

\begin{center}
\textbf{\Large Seth Seokhee Han} \\
School of Arts \& Sciences, Dartmouth College, Hanover, NH \\
Phone: +1 (603) 276-5846 \textbar \; Email: \href{mailto:seth.s.han.29@dartmouth.edu}{seth.s.han.29@dartmouth.edu} \\
LinkedIn: \href{https://www.linkedin.com/in/seth-seokhee-han/}{linkedin.com/in/seth-seokhee-han}
\end{center}

\section*{\textbf{Education}}
\textbf{Dartmouth College}, Hanover, NH \hfill 2025 -- 2029 \\
Bachelor of Arts in Engineering Sciences (GPA: TBD/4.0)

\textbf{Cheongshim International Academy}, Gyeonggi-do, South Korea \hfill 2022 -- 2025 \\
Korean High School Diploma (GPA: 5.0/5.0)

\section*{\textbf{Research Experience}}
\begin{itemize}
    \item \textbf{Research Scientist}, Drice \hfill 2022 -- 2025
    \\Advisors: Dr. Hyunwook Chung \& Mr. Donghwan Shin
    \\Computer vision and drone-based black ice detection and mapping

    \item \textbf{Student Researcher}, Choengshim International Academy \hfill 2024 -- 2025
    \\Advisor: Mr. Donghwan Shin
    \\Gait-recognition based missing person identification using CCTV footage

    \item \textbf{Student Researcher}, Choengshim International Academy \hfill 2021 -- 2022
    \\Advisor: Dr. Hyunchang Hong
    \\Heavy metal absorption using used mushroom compost
\end{itemize}

\section*{\textbf{Professional Experience}}
\begin{itemize}
    \item \textbf{Co-Founder \& CIO}, Drice \hfill 2022 -- 2025
    \\Developed and patented an AI-powered drone system that detects black ice in real-time. Secured \$11K+ in R\&D funding from the Ministry of Science of Korea, Ministry of Education of Korea, POSCO DX, etc.

    \item \textbf{Data Analyst Intern (CTO Staff)}, Enuma, Inc. \hfill 2025 -- 2025
    \\Analyzed user log from B2G edtech products in global markets using SQL and Python.
    
    \item \textbf{Co-Founder \& CSO}, Justiz \hfill 2023 -- 2024
    \\Built a language analysis platform to detect malicious comments and help influencers pursue legal action or data-driven business decisions. Secured \$11K+ in R\&D funding from the Ministry of Science of Korea.

    \item \textbf{Research Assistant Intern (CEO Staff)}, Enuma, Inc. \hfill 2024 -- 2024
    \\Researched edtech industry trends to enhance educational games for slow learners, presenting findings biweekly to the CEO and the CPO. Assisted in developing government-certified digital English and Mathematics textbooks in South Korea.
\end{itemize}

\section*{\textbf{Journal Papers}}
\begin{itemize}
    \item J. OH\textsuperscript{\textdagger}, J. Moon\textsuperscript{\textdagger}, \underline{S. HAN\textsuperscript{\textdagger}}, and D. SHIN, “Real-Time Black Ice Detection in Drone View Using YOLOX”, \textit{J Stud Res}, vol. 13, no. 2, May 2024. DOI: 10.47611/jsrhs.v13i2.6831\\%
    (\textsuperscript{\textdagger}Co-first authors)
\end{itemize}

\section*{\textbf{Patents}}
\begin{itemize}
    \item J. Oh, H. Lee, S. Moon, and \underline{S. Han}, "Black Ice Identification and Warning System and Method Using Unmanned Aerial Vehicles," KR Patent 10-2681032, Jul. 04, 2024.
\end{itemize}

\section*{\textbf{Selected Scholarships \& Awards}}

\textbf{\textit{Scholarships}}
\begin{itemize}
    \item Presidential Science Scholarship of South Korea (merit-based full ride scholarship) \hfill 2025
    \item James and Agnes Kim Family Scholarship (Dartmouth Honorary Paired Scholarship) \hfill 2025 \\
\end{itemize}

\textbf{\textit{Awards}}
\begin{itemize}
    \item Finalist \& National Rep., Regeneron International Science \& Engineering Fair (ISEF) \hfill 2024
    \item Minister of Science Award \& Provincial Rep., National Science Contest in Engineering \hfill 2024
    \item Deputy Prime Minister/Minister of Education Award, STEAM R\&E in Engineering \hfill 2024
    \item 1st Place, Korea Science \& Engineering Fair (KSEF) in Computer Science \hfill 2024
    \item 3rd Place, POSCO DX AI Youth Challenge \hfill 2024
    \item 1st Place, Gyeonggi Science Contest in Engineering \hfill 2024
    \item School Merit Award: Experiment \& Research \hfill 2024
    \item School Merit Award: Giftedness in Science \hfill 2024
    \item 2nd Place, Korea Science \& Engineering Fair (KSEF) in Computer Science \hfill 2023
    \item 1st Place \& National Rep., Youth International Science Fair (YISF) in Env. Sci. \hfill 2022
    \item Deputy Prime Minister/Minister of Education Award, STEAM R\&E in Engineering \hfill 2022
    \item 2nd Place, Korea Science \& Engineering Fair (KSEF) in Env. Sci. \hfill 2022
    \item 2nd Place \& Provincial Rep., Korea Youth Startup Competition \hfill 2022
    \item Finalist \& Innovation Award, Promising Student Start-up Team 300+ \hfill 2022
    \item School Merit Award: Giftedness in Science \hfill 2022
    \item 2nd Place, Youth Science Club (YSC) in Env. Sci. \hfill 2021
\end{itemize}

\section*{\textbf{Selected Activities and Engagements}}
\begin{itemize}
    \item \textbf{Executive Board Member}, DartUP Dartmouth \hfill 2025 -- Present\\
    Organized Dartmouth’s Social Blueprint Challenge (SBC, Hult Prize campus round). Designed and led a social entrepreneurship curriculum for SBC participants \& 30+ associate members.

    \item \textbf{Magnuson First Year Fellow}, Magnuson Center for Entrepreneurship \hfill 2025 -- Present\\
    Selected as 1 of 15 for entrepreneurship and leadership training. Mentored by the Magnuson Student Leadership Board and Entrepreneurial Thinking \& Leadership Fellows.
\end{itemize}

\end{document}
